---
title: "Analysis Report"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(here)
library(RVAideMemoire)
library(scales)
library(stargazer)
library(knitr)
library(kableExtra)

## Load data
raw <- readRDS(here("data", "T2T Data for Pinder et al.rds"))

## Prepare Data
## Select relevant variables
df <- raw %>%
  
  # Create new variables
  mutate(bads_act = yb_bads_3 + yb_bads_4 + yb_bads_5 + yb_bads_7 + yb_bads_11 + yb_bads_12 + yb_bads_23,
         bads_avr = yb_bads_8 + yb_bads_9 + yb_bads_10 + yb_bads_13 + yb_bads_14 + yb_bads_15 + yb_bads_24 + yb_bads_25,
         cdi_mean = rowMeans(select(., contains("cdi")), na.rm = TRUE)) %>%
  
  # Select and rename relevant variables
  select(race_eth = pb_childethnicity,
         sex = pb_childsex,
         gender = pb_childgender,
         age = pb_childage,
         income = pb_income,
         ppd_perm = yb_permanence,
         ppd_brain = yb_cause_brain,
         ppd_env = yb_cause_env,
         bads_act,
         bads_avr,
         cdi_mean) %>%
  
  # Drop NA
  drop_na(ppd_perm)
```

## Core Analysis

```{r}
# Prognostic Pessimism + BADS Activation
perm_act_cor <- cor.test(df$ppd_perm, df$bads_act, method = "spearman", exact = FALSE)
perm_act_cor_ci <- spearman.ci(df$ppd_perm, df$bads_act)

# Prognostic Pessimism + BADS Avoidance/Rumination
perm_avr_cor <- cor.test(df$ppd_perm, df$bads_avr, method = "spearman", exact = FALSE)
perm_avr_cor_ci <- spearman.ci(df$ppd_perm, df$bads_avr)
```

Prognostic pessimism is correlated with the BADS activation subscale at `r round(perm_act_cor$estimate, 3)` (_p_ = `r round(perm_act_cor$p.value, 3)`; 95% CI `r round(perm_act_cor_ci$conf.int[["Inf"]], 3)`, `r round(perm_act_cor_ci$conf.int[["Sup"]], 3)`)

Prognostic pessimism is correlated with the BADS avoidance/rumination subscale at `r round(perm_avr_cor$estimate, 3)` (_p_ = `r round(perm_avr_cor$p.value, 3)`; 95% CI `r round(perm_avr_cor_ci$conf.int[["Inf"]], 3)`, `r round(perm_avr_cor_ci$conf.int[["Sup"]], 3)`)

## Robustness Checks

#### Regressions

```{r, results = "asis"}
perm_act_lm <- lm(bads_act ~ ppd_perm, data = df)
perm_act_lm_controlled <- lm(bads_act ~ ppd_perm + cdi_mean, data = df)

perm_avr_lm <- lm(bads_avr ~ ppd_perm, data = df)
perm_avr_lm_controlled <- lm(bads_avr ~ ppd_perm + cdi_mean, data = df)

stargazer(perm_act_lm, perm_act_lm_controlled, perm_avr_lm, perm_avr_lm_controlled, type = "html")
```

#### Semi-Partial Correlations

```{r}
# Prognostic Pessimism + BADS Activation
perm_without_cdi <- lm(ppd_perm ~ cdi_mean, data = df) %>%
  pluck("residuals")

perm_act_spcor <- cor.test(perm_without_cdi, df$bads_act, method = "spearman", exact = FALSE)
perm_act_spcor_ci <- spearman.ci(perm_without_cdi, df$bads_act)

# Prognostic Pessimism + BADS Avoidance/Rumination
perm_avr_spcor <- cor.test(perm_without_cdi, df$bads_avr, method = "spearman", exact = FALSE)
perm_avr_spcor_ci <- spearman.ci(perm_without_cdi, df$bads_avr)
```

Prognostic pessimism is semi-partially correlated with the BADS activation subscale (after partialling CDI out of prognostic pessimism) at `r round(perm_act_spcor$estimate, 3)` (_p_ = `r round(perm_act_spcor$p.value, 3)`; 95% CI `r round(perm_act_spcor_ci$conf.int[["Inf"]], 3)`, `r round(perm_act_spcor_ci$conf.int[["Sup"]], 3)`)

Prognostic pessimism is semi-partially correlated with the BADS avoidance/rumination subscale (after partialling CDI out of prognostic pessimism) at `r round(perm_avr_spcor$estimate, 3)` (_p_ = `r round(perm_avr_spcor$p.value, 3)`; 95% CI `r round(perm_avr_spcor_ci$conf.int[["Inf"]], 3)`, `r round(perm_avr_spcor_ci$conf.int[["Sup"]], 3)`)