---
title: "Analysis Report"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(here)
library(RVAideMemoire)
library(scales)
library(stargazer)
library(knitr)
library(kableExtra)

## Load data
raw <- readRDS(here("data", "T2T Data for Pinder et al.rds"))

## Prepare Data
## Select relevant variables
df <- raw %>%
  
  # Create new variables
  mutate(bads_act = yb_bads_3 + yb_bads_4 + yb_bads_5 + yb_bads_7 + yb_bads_11 + yb_bads_12 + yb_bads_23,
         bads_avr = yb_bads_8 + yb_bads_9 + yb_bads_10 + yb_bads_13 + yb_bads_14 + yb_bads_15 + yb_bads_24 + yb_bads_25,
         cdi_mean = rowMeans(select(., contains("cdi")), na.rm = TRUE)) %>%
  
  # Select and rename relevant variables
  select(race_eth = pb_childethnicity,
         sex = pb_childsex,
         gender = pb_childgender,
         age = pb_childage,
         income = pb_income,
         ppd_perm = yb_permanence,
         ppd_brain = yb_cause_brain,
         ppd_env = yb_cause_env,
         bads_act,
         bads_avr,
         cdi_mean) %>%
  
  # Drop NA
  drop_na(ppd_perm)
```

## Core Analysis

```{r}
# Prognostic Pessimism + BADS Activation
perm_act_cor <- cor.test(df$ppd_perm, df$bads_act, method = "spearman", exact = FALSE)
perm_act_cor_ci <- spearman.ci(df$ppd_perm, df$bads_act)

# Prognostic Pessimism + BADS Avoidance/Rumination
perm_avr_cor <- cor.test(df$ppd_perm, df$bads_avr, method = "spearman", exact = FALSE)
perm_avr_cor_ci <- spearman.ci(df$ppd_perm, df$bads_avr)
```

Prognostic pessimism is correlated with the BADS activation subscale at `r round(perm_act_cor$estimate, 3)` (_p_ = `r round(perm_act_cor$p.value, 3)`; 95% CI `r round(perm_act_cor_ci$conf.int[["Inf"]], 3)`, `r round(perm_act_cor_ci$conf.int[["Sup"]], 3)`)

Prognostic pessimism is correlated with the BADS avoidance/rumination subscale at `r round(perm_avr_cor$estimate, 3)` (_p_ = `r round(perm_avr_cor$p.value, 3)`; 95% CI `r round(perm_avr_cor_ci$conf.int[["Inf"]], 3)`, `r round(perm_avr_cor_ci$conf.int[["Sup"]], 3)`)

## Robustness Checks

#### Regressions

```{r, results = "asis"}
perm_act_lm <- lm(bads_act ~ ppd_perm, data = df)
perm_act_lm_controlled <- lm(bads_act ~ ppd_perm + cdi_mean, data = df)

perm_avr_lm <- lm(bads_avr ~ ppd_perm, data = df)
perm_avr_lm_controlled <- lm(bads_avr ~ ppd_perm + cdi_mean, data = df)

stargazer(perm_act_lm, perm_act_lm_controlled, perm_avr_lm, perm_avr_lm_controlled, type = "html")
```

#### Semi-Partial Correlations

```{r}
# Prognostic Pessimism + BADS Activation
perm_without_cdi <- lm(ppd_perm ~ cdi_mean, data = df) %>%
  pluck("residuals")

perm_act_spcor <- cor.test(perm_without_cdi, df$bads_act, method = "spearman", exact = FALSE)
perm_act_spcor_ci <- spearman.ci(perm_without_cdi, df$bads_act)

# Prognostic Pessimism + BADS Avoidance/Rumination
perm_avr_spcor <- cor.test(perm_without_cdi, df$bads_avr, method = "spearman", exact = FALSE)
perm_avr_spcor_ci <- spearman.ci(perm_without_cdi, df$bads_avr)
```

Prognostic pessimism is semi-partially correlated with the BADS activation subscale (after partialling CDI out of prognostic pessimism) at `r round(perm_act_spcor$estimate, 3)` (_p_ = `r round(perm_act_spcor$p.value, 3)`; 95% CI `r round(perm_act_spcor_ci$conf.int[["Inf"]], 3)`, `r round(perm_act_spcor_ci$conf.int[["Sup"]], 3)`)

Prognostic pessimism is semi-partially correlated with the BADS avoidance/rumination subscale (after partialling CDI out of prognostic pessimism) at `r round(perm_avr_spcor$estimate, 3)` (_p_ = `r round(perm_avr_spcor$p.value, 3)`; 95% CI `r round(perm_avr_spcor_ci$conf.int[["Inf"]], 3)`, `r round(perm_avr_spcor_ci$conf.int[["Sup"]], 3)`)


#### Demographics

```{r}
# Get descriptives
df %>%
  count(age) %>%
  mutate(pct = percent(n / sum(n)))

df %>%
  count(income) %>%
  mutate(pct = percent(n / sum(n)))

df <- df %>% 
  mutate(race_eth = recode(
    race_eth,
    "American Indian and/or Alaska Native" = "AI/AN",
    "Black or African American" = "Black",
    "More than one race" = "Other/Mult",
    "White, non-Hispanic (includes Middle Eastern)" = "White",
    "Asian (including Asian Desi and Pacific Islander)" = "AA/PI",
    "Hispanic or Latino/a" = "Hisp/Lat",
    "Other, please specify" = "Other/Mult"))
df %>%
  count(race_eth) %>%
  mutate(pct = percent(n / sum(n)))

df = df %>% mutate(gender = case_when(
  sex == "female" & gender == "Woman" ~ "Cis Woman",
  sex == "male" & gender == "Man" ~ "Cis Man",
  TRUE ~ "Other"))
df %>%
  count(gender) %>%
  mutate(pct = percent(n / sum(n)))
# Remove original sex variable & reorder columns
dat1 <- subset(dat1, select = c("ppd_perm", "ppd_brain", "ppd_env",
                                "bads_act", "bads_avr",
                                "race_eth", "gender", "age", "income"))
```

#### Figure 1

```{r}
df_figure_1 <- df %>%
  select(ppd_perm, bads_act, bads_avr) %>%
  pivot_longer(c(bads_act, bads_avr),
               names_to = "bads_subscale",
               values_to = "bads_value") %>%
  drop_na() %>%
  group_by(ppd_perm, bads_subscale) %>%
  summarize(mean = mean(bads_value),
            sd = sd(bads_value),
            n = n()) %>%
  mutate(se = sd / sqrt(n),
         ci_95 = se * 1.96,
         bads_subscale = case_when(bads_subscale == "bads_act" ~ "BADS: Activation",
                                   bads_subscale == "bads_avr" ~ "BADS: Avoidance/Rumination"))

theme_CTR <- theme_classic() +
  theme(plot.title = element_text(size = 12),
        plot.subtitle = element_text(size = 12),
        axis.title = element_text(size = 12),
        axis.text = element_text(size = 12),
        strip.text = element_text(size = 12))
```

Option 1: Means and 95% Confidence Intervals

```{r}
ggplot(df_figure_1) +
  geom_point(aes(ppd_perm, mean)) +
  geom_errorbar(aes(ppd_perm, ymin = mean - ci_95, ymax = mean + ci_95)) +
  scale_x_continuous(name = "Prognostic Pessimism",
                     breaks = c(1, 5),
                     labels = c("Not at all Permanent", "Completely Permanent")) +
  scale_y_continuous(name = "BADS Sum Score") +
  facet_wrap(~ bads_subscale, ncol = 1, scales = "free_y") +
  ggtitle("BADS Subscale Scores by Prognostic Pessimism",
          "Means and 95% Confidence Intervals") +
  theme_CTR
```

Option 2: Means and Standard Errors

```{r}
ggplot(df_figure_1) +
  geom_point(aes(ppd_perm, mean)) +
  geom_errorbar(aes(ppd_perm, ymin = mean - se, ymax = mean + se)) +
  scale_x_continuous(name = "Prognostic Pessimism",
                     breaks = c(1, 5),
                     labels = c("Not at all Permanent", "Completely Permanent")) +
  scale_y_continuous(name = "BADS Sum Score") +
  facet_wrap(~ bads_subscale, ncol = 1, scales = "free_y") +
  ggtitle("BADS Subscale Scores by Prognostic Pessimism",
          "Means and Standard Errors") +
  theme_CTR
```

Option 1: Distributions with Means

```{r}
df %>%
  select(ppd_perm, bads_act, bads_avr) %>%
  pivot_longer(c(bads_act, bads_avr),
               names_to = "bads_subscale",
               values_to = "bads_value") %>%
  mutate(bads_subscale = case_when(bads_subscale == "bads_act" ~ "BADS: Activation",
         bads_subscale == "bads_avr" ~ "BADS: Avoidance/Rumination")) %>%
  drop_na() %>%
  ggplot() +
    geom_point(aes(ppd_perm, bads_value), 
               position = position_jitter(width = .1),
               alpha = .2) +
    stat_summary(aes(ppd_perm, bads_value),
                 fun = mean,
                 size = 1) +
    scale_x_continuous(name = "Prognostic Pessimism",
                       breaks = c(1, 5),
                       labels = c("Not at all Permanent", "Completely Permanent")) +
    scale_y_continuous(name = "BADS Sum Score") +
    facet_wrap(~ bads_subscale, ncol = 1, scales = "free_y") +
    ggtitle("BADS Subscale Scores by Prognostic Pessimism",
            "Distributions and Means") +    
    theme_CTR
```